Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-14 ms.tex
ready to send to coauthors

\title{Stellar and Planetary Properties of \KT\ \Ci\
Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving
Earth-like Insolation}

@@

\section{Introduction}
The \kep\ telescope \citep{Borucki10} has led to a revolution in stellar and planetary
astrophysics, with 7305 ``objects of interest'' and 4173 ``planet candidates''
discovered to date \citep{Borucki11a, Borucki11b, Batalha13, Burke14, Rowe15, Mullaly15}.
The fidelity of this sample is high, so most of these planet candidates are truly planets
\citep{Morton11b, Fressin13}.
The demise of two reaction wheels on the spacecraft led to a repurposing
of the spacecraft into the \KT\ mission, in which the telescope points at
fields near the ecliptic plane for $\sim 75$ days at a time \citep{Howell14}.
In this observing strategy, two axes of motion of the spacecraft are
controlled by the two remaining reaction wheels, while the roll of the
spacecraft is balanced with solar radiation pressure and quasiperiodic
thruster firing.
The result of this observing strategy is that the targets appear to drift
at the rate of $\sim 1\arcsec$ s$^{-1}$, with rapid corrections that occur
approximately once every six hours.
Over the full duration of each campaign, the targets appear to remain near the
same location on the detector but both the slow drift and the corrections are
observable by eye \citep{Barentsen15}.

@@

In this work, we use grids from the Dartmouth Stellar
Evolution Database \citep{Dotter08} at solar values of \afe=$0.0$ and
helium abundance $Y=0.2741$, which come packaged with the \texttt{isochrones}
module.  
We then run an MCMC chain using \texttt{emcee} \citep{Foreman-Mackey12},
an implementation of the affine-invariant ensemble sampler of 
\citet{Goodman10}
for each host star conditioned on the observed 
photometric properties as presented in Table 1.

@@

In order to try to encapsulate the effect of model uncertainties, we also run 
MCMC chains with photometric errors inflated artificially by a factor of three.  
We provide full chains using both inflated and un-inflated uncertainties, 
though in the rest of this work we adopt
the results obtained using the inflated values.

@@

The full list of stellar parameters adopted in this paper is included in
Tables 2 and 3. The former lists parameters derived from photometry with
un-inflated uncertainties, while the latter includes this inflating intended to
encapsulate the effect of model uncertainties.
% For some reason I can't get it to identify the table \ref here.
% If anyone can figure it out, be my guest!

@@

To derive the physical planet parameters conditioned on the measured stellar
parameters, we used the posterior probability distribution for quantities
measured using the light curve---from \paperit---and re-weighted them using
the results of the photometric and spectroscopic analysis.
In \paperit, the authors generated MCMC samples from the posterior
probability distribution over all the physical parameters (including stellar
mass and radius, and the planet radius) using broad, un-informative priors on
the values that are not constrained by the light curve.
As described in SOME APPENDIX, these samples can be re-weighted and used to
evaluate the posterior probability of the physical parameters of the planets
conditioned on the stellar values.
This also means that the effects of different measurements of the stellar
parameters can be easily tested by applying the method described in THAT SAME
APPENDIX.

The key assumption of this method is that the likelihood function used in
\paperit\ is correct.
That model was an exposure-time integrated, limb darkened light curve
\citep{Mandel02,Kipping10b} marginalized over the parameters of the
data-driven model of the instrumental systematics described in \paperit.

The results are given in SOME TABLE.

@@

Table \ref{Table:FPP} summarizes the results of these
calculations, presenting the relative probability for each candidate
to be caused by any of three false positive scenarios: an undiluted
eclipsing binary (EB), a hierarchical triple eclipsing binary (HEB),
and a chance-aligned background(/foreground) eclipsing binary (BEB).

@@

To investigate the possibility that such wide companions exist,
we query the ninth data release of the Sloan Digital Sky Survey
\citep[SDSS DR9,][]{Ahn12}.
For each target, we return
all stars within 12\arcsec with $\Delta r < 8$ relative to each object
of interest.
Of the 31 stars in our sample, four have such a companion.
Unlike the original \kep\ field, the field for \KT\ \Ci\ is
well out of the galactic plane, so the rate of giant, distanct background
stars is significantly lower.
We include a list of these potential contaminants as Table
6.

In Table 6, the ``maximum depth'' column represents
the maximum observed ``transit'' depth if the transit were actually caused
by a total eclipse of the hypothetical background binary system, inducing
a 50\% flux decrement in the background star's apparent brightness.

@@

\include{table_stellarprops_inflated}

>>>>

\title{Stellar and Planetary Properties of \KT\ Campaign 1
Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving
Earth-like Insolation}

@@

\section{Introduction}
The \kep\ telescope \citep{Borucki10} has led to a revolution in stellar and planetary
astrophysics, with 7305 ``objects of interest'' and 4173 ``planet candidates''
discovered to date \citep{Borucki11a, Borucki11b, Batalha13, Burke14, Rowe15, Mullaly15}.
The fidelity of this sample is high, so most of these planet candidates are truly planets
\citep{Morton11b, Fressin13}.
The demise of two reaction wheels on the spacecraft led to a repurposing
of the spacecraft into the \KT\ mission, in which the telescope points at
fields near the ecliptic plane for $\sim 75$ days at a time \citep{Howell14}.
In this observing strategy, two axes of motion of the spacecraft are
controlled by the two remaining reaction wheels, while the roll of the
spacecraft is balanced with solar radiation pressure and quasiperiodic
thruster firing.
The result of this observing strategy is that the targets appear to drift
at the rate of $\sim 1\arcsec$ hr$^{-1}$, with rapid corrections that occur
approximately once every six hours.
Over the full duration of each campaign, the targets appear to remain near the
same location on the detector but both the slow drift and the corrections are
observable by eye \citep{Barentsen15}.

@@

In this work, we use grids from the Dartmouth Stellar
Evolution Database \citep{Dotter08} at solar values of \afe=$0.0$ and
helium abundance $Y=0.2741$, which come packaged with the \texttt{isochrones}
module.  
We then run an MCMC chain using \texttt{emcee} \citep{Foreman-Mackey12},
an implementation of the affine-invariant ensemble sampler of 
\citet{Goodman10}
for each host star conditioned on the observed 
photometric properties as presented in Table 1.
We include a prior on stellar metallicity representative of the observed metallicities
of stars within 1 kpc of the Sun, following the results of \citet{Hayden15}.

@@

In order to try to encapsulate the effect of model uncertainties, we also run 
MCMC chains with photometric errors inflated artificially by a factor of three.  
We provide full chains using both inflated and un-inflated uncertainties, 
though in the rest of this work (and in Table 2) we adopt
the results obtained using the inflated values.

@@

The full list of stellar parameters adopted in this paper is included in
Table 2.
% For some reason I can't get it to identify the table \ref here.
% If anyone can figure it out, be my guest!

@@

To derive the physical planet parameters conditioned on the measured stellar
parameters, we used the posterior probability distribution for quantities
measured using the light curve---from \paperit---and re-weighted them using
the results of the photometric and spectroscopic analysis.
In \paperit, the authors generated MCMC samples from the posterior
probability distribution over all the physical parameters (including stellar
mass and radius, and the planet radius) using broad, un-informative priors on
the values that are not constrained by the light curve.
As described in the Appendix, these samples can be re-weighted and used to
evaluate the posterior probability of the physical parameters of the planets
conditioned on the stellar values.
This also means that the effects of different measurements of the stellar
parameters can be easily tested by applying the method described in 
Appendix A.
The key assumption of this method is that the likelihood function used in
\paperit\ is correct.
That model was an exposure-time integrated, limb darkened light curve
\citep{Mandel02,Kipping10b} marginalized over the parameters of the
data-driven model of the instrumental systematics described in \paperit.

The results are given in Table 3.

@@

Table 4 summarizes the results of these
calculations, presenting the relative probability for each candidate
to be caused by any of three false positive scenarios: an undiluted
eclipsing binary (EB), a hierarchical triple eclipsing binary (HEB),
and a chance-aligned background(/foreground) eclipsing binary (BEB).

@@

To investigate the possibility that such wide companions exist,
we query the ninth data release of the Sloan Digital Sky Survey
\citep[SDSS DR9,][]{Ahn12}.
For each target, we return
all stars within 12\arcsec with $\Delta r < 8$ relative to each object
of interest.
Of the 31 stars in our sample, four have such a companion.
Unlike the original \kep\ field, the field for \KT\ \Ci\ is
well out of the galactic plane, so the rate of giant, distanct background
stars is significantly lower.
We include a list of these potential contaminants as Table 5.

In Table 5, the ``maximum depth'' column represents
the maximum observed ``transit'' depth if the transit were actually caused
by a total eclipse of the hypothetical background binary system, inducing
a 50\% flux decrement in the background star's apparent brightness.

@@
